---
title: "eds 212 Day 5 a"
author: "Eva Newby"
format: html
execute: 
  warning: false
editor: visual
editor_options: 
  chunk_output_type: console
---

## 
```{r}
#| message: false
# load libraries ----
library(tidyverse)
```

`head(), `tail() and `dim()

```{r}
#| include: false

# do some data exploration with the star wars data frame ----
head(starwars, n = 8)

tail(starwars)

dim(starwars)
```

Create a ggplot(scatterplot) of character mass on the y axis and height on the x axis.
- update the color of the points so that color changes based on the value of `mass` 
```{r}
#| echo: false

ggplot(data=starwars, aes(x= height, y = mass, color = mass)) + geom_point() +
  labs(x = "Height (cm)", 
       y = "Mass (kg)", 
       title = "Here is my title")

```

- create a histogram of character heights 
- update the fill color (`fill`) to purple and the outside border line of each histogram bin (`color`) to orange 
- update axis labels
- updae your code chunk options so that only your code and output graph appear in rendered document (no warnings or messages)

```{r}
#| echo: false 
#| fig-cap: "This is my figure caption"
#| fig-alt: "This is some alt text"
ggplot(data=starwars, aes(x= height)) + 
         geom_histogram(fill = "purple", color = "orange") +
  labs(x= "Character Height (cm)",
       y = "Count")
```

`df$col_name`

```{r}
sw_height_mean <- round(mean(starwars$height, na.rm = TRUE), 3)

```
the mean height of all starwars characters is `r sw_height_mean`
